---
title: "MovieRecommender"
output: html_document
---

There are two types of recommendation systems – Content-Based Recommendation System and Collaborative Filtering Recommendation. In this project of recommendation system in R, we will work on a collaborative filtering recommendation system and more specifically, ITEM based collaborative recommendation system.

```{r}
library(recommenderlab)
library(ggplot2)                     
library(data.table)
library(reshape2

movie_data <- read.csv("movies.csv",stringsAsFactors=FALSE)
rating_data <- read.csv("ratings.csv")
#You can download the both datasets from https://drive.google.com/file/d/1Dn1BZD3YxgBQJSIjbfNnmCFlDW2jdQGD/view
```

```{r}
dim(movie_data)
str(movie_data)
summary(movie_data)
head(movie_data, 3)
```

```{r}
dim(rating_data)
str(rating_data)
summary(rating_data)
head(rating_data,3)
```

We will first create a one-hot encoding to create a matrix that comprises of corresponding genres for each of the films.

```{r}
movie_genre <- as.data.frame(movie_data$genres, stringsAsFactors = FALSE)
movie_genre2 <- as.data.frame(tstrsplit(movie_genre[,1], "[|]", type.convert = TRUE),
                              stringAsFactors = FALSE)

colnames(movie_genre2) <- c(1:10)

list_genre <- c("Action", "Adventure", "Animation", "Children", 
                "Comedy", "Crime","Documentary", "Drama", "Fantasy",
                "Film-Noir", "Horror", "Musical", "Mystery","Romance",
                "Sci-Fi", "Thriller", "War", "Western")

genre_mat1 <- matrix(0,10330,18)
genre_mat1[1,] <- list_genre
colnames(genre_mat1) <- list_genre

for (index in 1:nrow(movie_genre2)) {
  for (col in 1:ncol(movie_genre2)) {
    gen_col = which(genre_mat1[1,] == movie_genre2[index,col]) 
    genre_mat1[index+1,gen_col] <- 1
  }}

genre_mat2 <- as.data.frame(genre_mat1[-1,], stringsAsFactors=FALSE) #remove first row, which was the genre list
for (col in 1:ncol(genre_mat2)) {
  genre_mat2[,col] <- as.integer(genre_mat2[,col]) #convert from characters to integers
} 
str(genre_mat2)

```

After this process, we will create a ‘search matrix’ that will allow us to perform an easy search of the films by specifying the genre present in our list.

```{r}

SearchMatrix <- cbind(movie_data[,1:2], genre_mat2[])
head(SearchMatrix)
dim(SearchMatrix)


```

After that, we have to convert our matrix into a sparse matrix one. This new matrix is of the class ‘realRatingMatrix’.
```{r}
ratingMatrix <- dcast(rating_data, userId~movieId, value.var = "rating", na.rm=FALSE)
ratingMatrix <- as.matrix(ratingMatrix[,-1]) #remove userIds
#Convert rating matrix into a recommenderlab sparse matrix
ratingMatrix <- as(ratingMatrix, "realRatingMatrix")
ratingMatrix
```

```{r}
recommendation_model <- recommenderRegistry$get_entries(dataType = "realRatingMatrix")
names(recommendation_model)
```

```{r}
lapply(recommendation_model, "[[", "description")
```

As we said at the beginning, We will implement a single model in our R project – Item Based Collaborative Filtering.

```{r}

recommendation_model$IBCF_realRatingMatrix$parameters

```

Collaborative Filtering involves suggesting movies to the users that are based on collecting preferences from many other users. For example, if a user A likes to watch action films and so does user B, then the movies that the user B will watch in the future will be recommended to A and vice-versa. Therefore, recommending movies is dependent on creating a relationship of similarity between the two users. With the help of recommenderlab, we can compute similarities using various operators like cosine, pearson as well as jaccard.

```{r}
similarity_mat <- similarity(ratingMatrix[1:4, ],
                               method = "cosine",
                               which = "users")
as.matrix(similarity_mat)
image(as.matrix(similarity_mat), main = "User's Similarities")
```

```{r}
movie_similarity <- similarity(ratingMatrix[, 1:4], method =
                                 "cosine", which = "items")
as.matrix(movie_similarity)
image(as.matrix(movie_similarity), main = "Movies similarity")
```

Let us now extract the most unique ratings 
```{r}
rating_values <- as.vector(ratingMatrix@data)
unique(rating_values)
```

```{r}
Table_of_Ratings <- table(rating_values) # creating a count of movie ratings
Table_of_Ratings
```

DATA VISUALIZATION PART

```{r}
movie_views <- colCounts(ratingMatrix) # count views for each movie
table_views <- data.frame(movie = names(movie_views),
                          views = movie_views) # create dataframe of views
table_views <- table_views[order(table_views$views,
                                 decreasing = TRUE), ] # sort by number of views
table_views$title <- NA
for (index in 1:10325){
  table_views[index,3] <- as.character(subset(movie_data,
                                         movie_data$movieId == table_views[index,1])$title)
}
table_views[1:6,]
```
```{r}
ggplot(table_views[1:6, ], aes(x = title, y = views)) +
  geom_bar(stat="identity", fill = 'steelblue') +
  geom_text(aes(label=views), vjust=-0.3, size=3.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Total Views of the Top Films")
```

```{r}
image(ratingMatrix[1:20, 1:25], axes = FALSE, main = "Heatmap of the first 25 rows and 25 columns")
```






































